---
title: "Stat 330 Final Project Proposal"
authors: Jose De Leon and Ethan Clayburn
format: 
  pdf:
    embed-resources: true 
---


<style type="text/css">
h1.title {
  font-size: 40px;
  text-align: center;
}
</style>


```{r setup, include=FALSE}
library(tidyverse)
library(readxl)
```

# 1 Group Members

The group members are Jose De Leon and Ethan Clayburn

# 2 Data Set

DELETE THIS: What dataset do you intend to use for your final project? Where can it be found? **Provide a description of the data set and the variables it contains.** Load your data into R and print the first few rows of the data set.

```{r}
baseball <- read_delim("Data", delim = ",")
head(baseball)
```


# 3 Potential Questions of Interest

DELETE THIS: What are two scientific questions you could try to answer by applying regression tools to this dataset? **Provide commentary on why someone might be interested in studying these questions.**

# 4 Exploratory Data Analysis

DELETE THIS: Conduct EDA and provide **at least 3** figures or statistics highlighting features or between variable relationships within the data that are relevant to the questions of interest you provided earlier in the proposal. **You should explain what you found interesting or noteworthy about each of 3 included elements.**
```{r}
#Code for your EDA here. 
#Can you come up with useful visualizations of your data 
#that might help someone gain insight into your questions of interest 
#prior to any formal statistical analysis being conducted?
```

# 5 Preliminary Model Fit

DELETE THIS: Select a variable from your dataset that makes sense to describe as a dependent or response variable, and another to describe as an explanatory or predictor variable.

DELETE THIS: **Write out the model you have chosen** and fit it using R. The SLR model you fit doesn't have to directly relate to one of your research questions, but **you should provide a brief justification of why someone may be interested in the relationship characterized by your initial model.**

```{r}
#lm.fit = lm(response~predictor, data = proj_data)
```

DELETE THIS: Assess whether the regression assumptions are satisfied **and provide interpretation for the estimated model coefficients and associated uncertainty estimates.** You are welcome to use as many or as few code blocks as you wish in this section, but make sure that your analysis is easy to follow.

```{r}
#Assess assumptions

#Interpret model output contained in summary(lm.fit)
```

